Instant Continuation Marks--Just Add $\lambda$

### 2012-10-05 paper.tex
Put example in with JIT expansion.

The formal transformation of a \scheme'wcm' directive is also extremely similar to the \scheme'let' version. The definition of \scheme'C[cons]' is unfolded and simplified.
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    ((C[body-expr] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[mark-expr] FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (kont)
  (lambda (flag)
    (lambda (marks)
      (((Ccps[mark-expr]
          (lambda (mark-value) 
            ((lambda (rest-marks) 
               (((Ccps[body-expr] kont) TRUE) (lambda (z) C[((z mark-value) rest-marks)])))
             ((flag Ch_cps[(SND marks)]) marks))))
        FALSE)
       marks))))
\end{schemedisplay}
\end{schemedefn}

@@

Consider the \cm\ program \scheme|(wcm 0 ((lambda (x) (wcm x (ccm))) 1))| which reduces as
\begin{schemedisplay}
(wcm 0 ((lambda (x) (wcm x (ccm))) 1))
(wcm 0 (wcm 1 (ccm)))
(wcm 1 (ccm))
(wcm 1 (lambda (z) ((z 1) (lambda (x) (lambda (y) y)))))
(lambda (z) ((z 1) (lambda (x) (lambda (y) y))))
\end{schemedisplay}
and transforms as
\begin{schemedisplay}
Ch[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))]
((C[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))] FALSE) Cp[NIL])
(((lambda (flag)
  (lambda (marks)
    ((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[0] FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
 FALSE)
Cp[NIL])
(((lambda (flag)
  (lambda (marks)
    ((C[(lambda (flags)
  (lambda (marks)
    (((((C[(lambda (x) (wcm x (ccm)))] FALSE) marks)
       ((C[1] FALSE) marks))
      flags)
     marks)))] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       (((lambda (flag) (lambda (marks) 0)) FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
 FALSE)
Cp[NIL])
(((lambda (flag)
  (lambda (marks)
    ((C[(lambda (flags)
  (lambda (marks)
    ((((((lambda (flag)
           (lambda (marks)
             (lambda (x)
               C[(wcm x (ccm))]))) FALSE) marks)
       (((lambda (flag) (lambda (marks) 1)) FALSE) marks))
      flags)
     marks)))] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       (((lambda (flag) (lambda (marks) 0)) FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
 FALSE)
Cp[NIL])
(((lambda (flag)
  (lambda (marks)
    ((C[(lambda (flags)
  (lambda (marks)
    ((((((lambda (flag)
           (lambda (marks)
             (lambda (x)
               (lambda (flag)
  (lambda (marks)
    ((C[(ccm)] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[x] FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))))) FALSE) marks)
       (((lambda (flag) (lambda (marks) 1)) FALSE) marks))
      flags)
     marks)))] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       (((lambda (flag) (lambda (marks) 0)) FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
 FALSE)
Cp[NIL])

(((lambda (flag)
  (lambda (marks)
    ((C[(lambda (flags)
  (lambda (marks)
    ((((((lambda (flag)
           (lambda (marks)
             (lambda (x)
               (lambda (flag)
  (lambda (marks)
    (((lambda (flag) (lambda (marks) marks)) TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       (((lambda (flag) (lambda (marks) x)) FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))))) FALSE) marks)
       (((lambda (flag) (lambda (marks) 1)) FALSE) marks))
      flags)
     marks)))] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       (((lambda (flag) (lambda (marks) 0)) FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
 FALSE)
Cp[NIL])
\end{schemedisplay}

>>>>

The formal transformation of a \scheme'wcm' directive is also extremely similar to the \scheme'let' version. The definition of \scheme'C[cons]' is unfolded and simplified.
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    ((C[body-expr] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)])))
       ((C[mark-expr] FALSE) marks))
      ((flag Ch[(SND marks)]) marks)))))
\end{schemedisplay}
\end{schemedefn}

@@

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (kont)
  (lambda (flag)
    (lambda (marks)
      (((Ccps[mark-expr]
          (lambda (mark-value) 
            ((lambda (rest-marks) 
               (((Ccps[body-expr] kont) TRUE) Cp[((CONS mark-value) rest-marks)])))
             ((flag Ch_cps[(SND marks)]) marks))))
        FALSE)
       marks))))
\end{schemedisplay}
\end{schemedefn}

@@

Consider the \cm\ program \scheme|(wcm 0 ((lambda (x) (wcm x (ccm))) 1))| which reduces as
\begin{schemedisplay}
(wcm 0 ((lambda (x) (wcm x (ccm))) 1))
(wcm 0 (wcm 1 (ccm)))
(wcm 1 (ccm))
(wcm 1 (lambda (z) ((z 1) (lambda (x) (lambda (y) y)))))
(lambda (z) ((z 1) (lambda (x) (lambda (y) y))))
\end{schemedisplay}
and transforms as
\begin{schemedisplay}
Ch[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))]

((C[(wcm 0 ((lambda (x) (wcm x (ccm))) 1))] FALSE) Cp[NIL])

(((lambda (flag)
    (lambda (marks)
      ((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
       (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
         ((C[0] FALSE) marks)) ((flag Ch[(SND marks)]) marks)))))
  FALSE) Cp[NIL])

((lambda (marks)
   ((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
    (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
      ((C[0] FALSE) marks)) ((FALSE Ch[(SND marks)]) marks))))
 Cp[NIL])

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((C[0] FALSE) Cp[NIL])) ((FALSE Ch[(SND NIL)]) Cp[NIL])))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   (((lambda (flag) (lambda (marks) 0)) FALSE) Cp[NIL])) ((FALSE Ch[(SND NIL)]) Cp[NIL])))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((lambda (marks) 0) Cp[NIL])) ((FALSE Ch[(SND NIL)]) Cp[NIL])))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   0) ((FALSE Ch[(SND NIL)]) Cp[NIL])))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 ((lambda (rest-marks) Cp[((CONS 0) rest-marks)])
  ((FALSE Ch[(SND NIL)]) Cp[NIL])))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE)
 ((lambda (rest-marks) Cp[((CONS 0) rest-marks)])
  Cp[NIL]))

((C[((lambda (x) (wcm x (ccm))) 1)] TRUE) Cp[((CONS 0) NIL)])

(((lambda (flag)
    (lambda (marks)
      (((((C[(lambda (x) (wcm x (ccm)))] FALSE) marks)
         ((C[1] FALSE) marks))
        flag)
       marks))) TRUE) Cp[((CONS 0) NIL)])

(((((C[(lambda (x) (wcm x (ccm)))] FALSE) Cp[((CONS 0) NIL)])
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

((((((lambda (flag) (lambda (marks) (lambda (x) C[(wcm x (ccm))]))) FALSE) Cp[((CONS 0) NIL)])
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

(((((lambda (marks) (lambda (x) C[(wcm x (ccm))])) Cp[((CONS 0) NIL)])
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

((((lambda (x) C[(wcm x (ccm))])
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

((((lambda (x) C[(wcm x (ccm))])
   (((lambda (flag) (lambda (marks) 1)) FALSE) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

((((lambda (x) C[(wcm x (ccm))])
   ((lambda (marks) 1) Cp[((CONS 0) NIL)]))
  TRUE) Cp[((CONS 0) NIL)])

((((lambda (x) C[(wcm x (ccm))])
   1) TRUE) Cp[((CONS 0) NIL)])

((C[(wcm 1 (ccm))]
   TRUE) Cp[((CONS 0) NIL)])

(((lambda (flag)
    (lambda (marks)
      ((C[(ccm)] TRUE)
       (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
         ((C[1] FALSE) marks))
        ((flag Ch[(SND marks)]) marks)))))
  TRUE) Cp[((CONS 0) NIL)])

((lambda (marks)
   ((C[(ccm)] TRUE)
    (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
      ((C[1] FALSE) marks))
     ((TRUE Ch[(SND marks)]) marks))))
 Cp[((CONS 0) NIL)])

((C[(ccm)] TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

(((lambda (flag) (lambda (marks) marks))
  TRUE)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((C[1] FALSE) Cp[((CONS 0) NIL)]))
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   (((lambda (flag) (lambda (marks) 1)) FALSE) Cp[((CONS 0) NIL)]))
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   ((lambda (marks) 1) Cp[((CONS 0) NIL)]))
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 (((lambda (mark-value) (lambda (rest-marks) Cp[((CONS mark-value) rest-marks)]))
   1)
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 ((lambda (rest-marks) Cp[((CONS 1) rest-marks)])
  ((TRUE Ch[(SND ((CONS 0) NIL))]) Cp[((CONS 0) NIL)])))

((lambda (marks) marks)
 ((lambda (rest-marks) Cp[((CONS 1) rest-marks)])
  Ch[(SND ((CONS 0) NIL))]))

((lambda (marks) marks)
 ((lambda (rest-marks) Cp[((CONS 1) rest-marks)])
  Cp[NIL]))

((lambda (marks) marks)
 Cp[((CONS 1) NIL)])

Cp[((CONS 1) NIL)]
\end{schemedisplay}
